Empirical normative theories

### 2020-07-26 simple.tex
Simpler commands and notation

Given $i \in I, \phi \in \Phi, \ar_0 \in \allargs$ and $\args \subseteq \gbeatsinv(\ar_0)$, define $\args \ibeatscoal \ar_0$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar_0) \cap \hist \land \ar_0 \in \histend \land \hist \nileadstost \phi$.

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \powersetz{\alldargs}$, as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \land \args \ibeatscoal \ar_0}$. 
Observe that $\di(\ar) \subseteq \df(\ar)$.
Define $\dip \subseteq \allargs × \allargs$ as $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$.
Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.

$\ar$ $i$-defends $\phi$ iff $\emptyset \nibeatscoal \ar$.

@@

	Lemma: if $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \dargs \in \di(\ar_0)$.
	Consider any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$ and $\ar_0 \nileadstost \phi$. 
	By definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$.
	Define $\args = \gbeatsinv(\ar_0) \cap \hist$. Thus, $\args \ibeatscoal \ar_0$.
	Also, because $\ar_0$ $i$-defends $\phi$, $\args ≠ \emptyset$. 
	Therefore, $\dbeatsinv(\args) \in \di(\ar_0)$.

@@

Note first that $\ar_0 \gbeats \ar_0$ is impossible because … TODO why didn’t I need this before?

>>>>

Given $i \in I, \phi \in \Phi, \ar_0 \in \allargs$ and $\args \subseteq \gbeatsinv(\ar_0)$, define $\args \ibeats \ar_0$ iff $\exists \hist \in \allhist \suchthat \args = \gbeatsinv(\ar_0) \cap \hist \land \ar_0 \in \histend \land \hist \nileadstost \phi$.

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \powersetz{\alldargs}$, as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar_0) \land \args \ibeats \ar_0}$. 
Observe that $\di(\ar) \subseteq \df(\ar)$.
Define $\dip \subseteq \allargs × \allargs$ as $\dip(\ar) = \set{(\ar + \dargs) \suchthat \dargs \in \di(\ar)}$.
Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$.

$\ar$ $i$-defends $\phi$ iff $\emptyset \nibeats \ar$.

@@

	Lemma: if $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \dargs \in \di(\ar_0)$.
	Consider any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$ and $\ar_0 \nileadstost \phi$. 
	By definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$.
	Define $\args = \gbeatsinv(\ar_0) \cap \hist$. Thus, $\args \ibeats \ar_0$.
	Also, because $\ar_0$ $i$-defends $\phi$, $\args ≠ \emptyset$. 
	Therefore, $\dbeatsinv(\args) \in \di(\ar_0)$.

@@
